# Results

Here is a table of the coefficients we get after fitting the models:

```{r, echo=FALSE}
suppressMessages(library(xtable))
load("data/Ridge-saved-objects.Rdata")
load("data/lasso-saved-objects.Rdata")
load("data/ols-saved-objects.Rdata")
load("data/pcr-saved-objects.Rdata")
load("data/pls-saved-objects.Rdata")

v <-as.vector(ols$coefficients)[-c(1)]
w <-as.vector(ridge_pred_full)[-c(1,2)]
x <-as.vector(lasso_pred_full)[-c(1,2)]
y <-as.vector(pcr_full_coefs)
z <-as.vector(pls_full_coefs)
coef_names<-c("Income", "Limit", "Rating", 
              "Cards", "Age", "Education", 
              "GenderFemale", "StudentYes", 
              "MarriedYes","EthnicityAsian",
              "EthnicityCaucasian")
names(v)<- coef_names
names(w)<- coef_names
names(x)<- coef_names
names(y)<- coef_names
names(z)<- coef_names
v_name <- "OLS"
w_name <- "Ridge"
x_name <- "LASSO"
y_name <- "PCR"
z_name <- "PLS"
df <- data.frame(v,w,x,y,z)
names(df)<-c(v_name,w_name,x_name,y_name,z_name)
coef_tbbl<-xtable(df, type="latex")
print(coef_tbbl)
```

This is a graphical representation of the coefficients:

```{r, echo=FALSE}
suppressMessages(library(ggplot2))
load("data/Ridge-saved-objects.Rdata")
load("data/lasso-saved-objects.Rdata")
load("data/ols-saved-objects.Rdata")
load("data/pcr-saved-objects.Rdata")
load("data/pls-saved-objects.Rdata")

v <-as.vector(ols$coefficients)[-c(1)]
w  <-append(v, as.vector(ridge_pred_full)[-c(1,2)],
           after = length(v))
x <-append(w, as.vector(lasso_pred_full)[-c(1,2)],
           after = length(w))
y <-append(x, as.vector(pcr_full_coefs),
           after = length(x))
z <-append(y, as.vector(pls_full_coefs),
           after = length(x))

a<-c("Income", "Limit", "Rating", 
              "Cards", "Age", "Education", 
              "GenderFemale", "StudentYes", 
              "MarriedYes","EthnicityAsian",
              "EthnicityCaucasian")
b<- c(rep(a, times=5))


h<- c(rep("OLS",times=11), rep("Ridge",times=11),
      rep("LASSO",times=11),rep("PCR",times=11),
      rep("PLS",times=11))


z_name <- "CoefficientValue"
b_name <- "Variable"
h_name <- "Model"
coeff_df <- data.frame(z,b,h)
names(coeff_df)<-c(z_name, b_name, h_name)

ggplot(data=coeff_df,aes(x=Variable,y=CoefficientValue))+
  geom_bar(stat = "identity")+
  facet_wrap(~Model)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Here are the MSE's of each regression:

```{r echo=FALSE}
suppressMessages(library(xtable))
load("data/Ridge-saved-objects.Rdata")
load("data/lasso-saved-objects.Rdata")
load("data/ols-saved-objects.Rdata")
load("data/pcr-saved-objects.Rdata")
load("data/pls-saved-objects.Rdata")

names(mse_ols)<-"MSE"
names(ridge_mse)<-"MSE"
names(lasso_mse)<-"MSE"
names(pcr_mse)<-"MSE"
names(pls_mse)<-"MSE"
mse_df<-data.frame(mse_ols,ridge_mse,lasso_mse,pcr_mse,pls_mse)
names(mse_df)<-c("OLS","Ridge", "LASSO","PCR","PLS")
mse_tbbl<-xtable(mse_df,type="latex")
print(mse_tbbl)
```

  
  For our analysis, 
  -ridge
  -lasso
  
  Principal Components Regression performed best with 10 components. The full model fit with this number of components resulted in an MSE of ≈ 0.046
  
  Partial Least Squares Regression performe best with  components. The model fit with this number of components resulted in an MSE of 

Thus, our best performing model, with an MSE of ____, is ______. 

Why is it that original least squares performed better than our other, more complicated methods? The four methods we discussed each have particular use-cases. For example, in cases where the data has a large number of variables, high colliniearity, or a we are seeking a sparse solution, the above techniques will work well. As these aren't necessarily what we're looking for with the Credit data, it's not very surprising that the strong method that is original least squares would perform well.

